HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-08-31 scnn.tex
small edit
size comparison with imagenet

A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs
\begin{equation*}
	\y = FC(\x) = \b W \x + \b b \in \R^{F_{out}} ,
\end{equation*}
where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \times F_{out}$ (or $N_{stat} \times F_{out}$).

@@

In all our experiments, we saw no sign of over-fitting.
With more data, HealpixNet can probably do even better.
The fact that the CNN lags behind the FCN is another sign of lack of data.

>>>>

The layer $FC: \R^{F_{in}} \rightarrow \R^{F_{out}}$ is defined as
\begin{equation} \label{eqn:fc_layer}
	\y = FC(\x) = \b W \x + \b b ,
\end{equation}
where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \times F_{out}$ (or $N_{stat} \times F_{out}$).

@@

We saw no sign of over-fitting in any of our experiments.
With more data, HealpixNet can probably do even better.
The fact that the CNN lags behind the FCN is another sign of lack of data.
ImageNet, the largest dataset for visual object recognition, features about 900 billion pixels ($14 \times 10^6 \times 256^2$), to be compared with the 750 millions pixels ($60 \times 12 \times 1024^2$) of our dataset.
